
	\documentclass{res}
	\usepackage{fancyhdr}
	\usepackage{fontspec}
	\usepackage{color}
	\usepackage{multicol}
	\usepackage{setspace}
	\usepackage{xcolor}
	\usepackage{hyperref}
	\usepackage{enumitem}
	\setlength{\textwidth}{6.5in}
	
	\newcommand{\HRule}{\rule{\linewidth}{0.25pt}}
	\newsectionwidth{0.25in}

	% format URLs
	\colorlet{ucolor}{yellow!14!black!14!red!72!}
	\urlstyle{same}
	\hypersetup{
		colorlinks=true,
		linkcolor=ucolor,
		urlcolor=ucolor
	}

	\pagestyle{fancy}
	\pagenumbering{arabic}

	\newcommand{\spacedsc}{\scshape\addfontfeatures{LetterSpace=15}}
	\renewcommand{\sectionfont}{\normalfont\Large\spacedsc\color{gray}\raggedright}
	\renewcommand{\headrulewidth}{0.0pt}
	
	\begin{document}

	\hspace*{-0.05\textwidth}
	\begin{minipage}[t]{0.6\textwidth}
	\begin{flushleft}
	\vspace*{\fill}
	{\fontsize{45}{45}\selectfont Pawan\textbf{Sutar}}
	\end{flushleft}
	\end{minipage}
	\begin{minipage}[t]{0.44\textwidth}
	\begin{flushright}
	\href{mailto:pawansutar@outlook.com}{pawansutar@outlook.com} \\ 
	\end{flushright}
	\end{minipage}

	\begin{resume}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{\MakeUppercase{About me}} \vskip 0.15in
	I am currently employed at [This Company]. Before this I was in graduate school at [This University] where I earned a PhD. in [Computer Science](https://www.cs.wisc.edu/) under the supervision of [This Professor].

**My interests:**
* Computer Graphics
* Develop web \& desktop applications
* Physics based Modeling and Simulations

[This University]: https://wisc.edu
[This Professor]: https://wisc.edu
[This Company]: https://github.com/acrlakshman/profileio
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Education}} \vskip 0.15in
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf MSME Computer Science} \hfill GPA: 3.90/4 \\
	{University of Wisconsin-Madison \hfill } \\ \\
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Work/Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Experience}} \vskip 0.15in
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\hspace*{-0.25in}{\bf Senior Software Engineer} \hfill 2019-Present \\
	\hspace*{-0.25in}{\it Combustion and Propulsion Research Laboratory, Indianapolis, IN}
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{0mm} \smallskip
	
		\item Sample text written as part of the demo for profileio. Sample text written as part of the demo for profileio
		\item This is the sample text written for the demo of profileio
	\end{itemize}
	
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% List: Custom[0] %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Patents}} \vskip 0.35in
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{6pt}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item ~~~~~~~~~~~~~~~~~~~~~~~~~~~%
		\item[] {\bf Physics based simulations:} Level set method I for artistic simulations (9999998). Level set method II for artistic simulations (9999999).
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item ~~~~~~~~~~~~~~~~~~~~~~~~~~~%
		\item[] {\bf Experimental physics:} Novel PIV method to quatify velocity of fluid flow through swirl atomizer (9999997)
	\end{itemize}
	
		
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Projects}} \vskip 0.15in
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\hspace*{-0.25in}{\bf ProfileIO} \\
	\hspace*{-0.25in}\_with [Lakshman Anumolu](//lakshmananumolu.com)\_ \hfill 2020-Present
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Website and resume generator via YAML
	\end{itemize}
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Publications %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Publications}} \vskip 0.35in
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{4pt}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] \href{https://www.sciencedirect.com/science/article/pii/S0021999117307696}{Made-up title of an article for ProfileIO' demo}, **Author I**, Author II, Journal of Computational Physics, 353:377-406, 2018.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 1 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] \href{https://www.worldscientific.com/doi/abs/10.1142/9789813229440_0008}{Sample title of a book made-up to give demo for profileio}, Author I, **Author II**, and Author III, volume 3 of Encyclopedia of Two-Phase Heat Transfer and Flow, World Scientific, 2018.
	\end{itemize}
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Work/Experience: Custom[2] %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Vocational Training}} \vskip 0.15in
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\hspace*{-0.25in}{\bf Trainee} \hfill 2014 \\
	\hspace*{-0.25in}{\it Animation Studios}
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{0mm} \smallskip
	
		\item This is the sample text written for the demo of profileio
		\item Sample text written as part of the demo for profileio
	\end{itemize}
	
	
		
	
	
	
	
	
	
	
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% List: Custom[1] %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\MakeUppercase{Skills}} \vskip 0.35in
	\begin{itemize}[leftmargin=\parindent]
	\setlength{\itemsep}{6pt}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item ~~~~~~~~~~~~~~~~~~~~~~~~~~~%
		\item[] {\bf Programming Languages:} Fluent: C++, C, Go. Experienced: Python, JavaScript, PHP
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item ~~~~~~~~~~~~~~~~~~~~~~~~~~~%
		\item[] {\bf Libraries:} Eigen, NumPy, MPI, etc.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Item ~~~~~~~~~~~~~~~~~~~~~~~~~~~%
		\item[] {\bf Tools:} CMake, gdb, valgrind, etc.
	\end{itemize}
	
		
	
	
	\end{resume}
	\end{document}
	